\begin{thebibliography}{1}
\bibitem{stm32u5}
STMicroelectronics,
\textit{STM32U5-series overview},
2023.
Available: \url{https://www.st.com/en/microcontrollers-microprocessors/stm32u5-series.html}

\bibitem{freertos}
Real Time Engineers Ltd.,
\textit{FreeRTOS Kernel Reference Manual},
2024.
Available: \url{https://www.freertos.org/Documentation/RTOS_book.html}

\bibitem{sx1276}
Semtech Corporation,
\textit{SX1276 LoRa Transceiver IC},
2025.
Available: \url{https://www.semtech.com/products/wireless-rf/lora-connect/sx1276}

\bibitem{espeakng}
eSpeak-NG, 
\textit{eSpeak NG -- Next Generation Text to Speech}, 
2025. 
Available: \url{https://github.com/espeak-ng/espeak-ng}

\bibitem{TPS629203}
STMicroelectronics,
\textit{Datasheet TPS629203}, 
2025. 
Available: \url{https://www.ti.com/product/TPS629203}

\bibitem{LoRa module}
HOPERF,
\textit{RFM96W overview}, 
2025. 
Available: \url{https://www.hoperf.com/modules/lora/RFM96W.html}

\bibitem{ADC}
STMicroelectronics,
\textit{Datasheet PCM1808}, 
2025. 
Available: \url{https://www.ti.com/lit/ds/symlink/pcm1808.pdf}

\bibitem{microphone design guide}
Texas Instruments,
\textit{Design example}, 
2025. 
Available: \url{https://www.ti.com/lit/an/sboa290a/sboa290a.pdf?ts=1747751396287}

\bibitem{DAC}
Texas Instruments,
\textit{Datasheet PCM5100A}, 
2025. 
Available: \url{https://www.ti.com/product/PCM5100A}

\bibitem{Lora-nbiot_paper}
KTH Royal institute of technolgy,
\textit{Comparison of LoRa and NBIoT in Terms of Power
Consumption}, 
2025. 
Available: \url{https://www.diva-portal.org/smash/get/diva2:1451892/FULLTEXT01.pdf?trk=public_post_comment-text}

\bibitem{LoRa-GPS-HAT}
Dragino,
\textit{LoRa GPS HAT for Raspberry Pi Manual},
2025.
available: \url{https://www.dragino.com/downloads/downloads/LoRa-GPS-HAT/LoRa_GPS_HAT_UserManual_v1.0.pdf}

\bibitem{tiny-AES}
Kokke,
\textit{Tiny AES in C},
2025.
Available: \url{https://github.com/kokke/tiny-AES-c}

\bibitem{stm32-hall-library}
belyalov,
\textit{STM32 HAL Library},
2025.
Available: \url{https://github.com/belyalov/stm32-hal-libraries/tree/master}

\bibitem{WiringPi}
WiringPi,
\textit{WiringPi Library},
2025.
Available: \url{https://github.com/WiringPi/WiringPi}

\bibitem{flutter}
Flutter,
\textit{Flutter SDK},
2025.
Available: \url{https://flutter.dev/docs/get-started/install}

\end{thebibliography}
